\cvsection{Experience}

\begin{cventries}
  \cventry
    {software engineering intern (full stack)} % Job title
    {Citadel LLC} % Organization
    {New York, NY} % Location
    {may - aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \vspace{1.0mm}
        \item {Developed and released a real-time financial data web-application in React and RxJS utilized by hundreds of analysts}
        \vspace{1.0mm}
        \item {Maintained and added data processing and visualization functionality to Java and Hapi.JS backend APIs}
      \end{cvitems}
    }
  \vspace{2.4mm}    
  \cventry
    {software engineering intern (data engineering)} % Job title
    {Scribd} % Organization
    {San Francisco, CA} % Location
    {sep. - dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \vspace{1.0mm}
        \item {Monitored and managed the data pipeline; maintained Hadoop jobs and handled content ingestion and parsing issues}
        \vspace{1.0mm}
        \item {Rewrote and optimized the two largest daily Hive tasks in Spark, reducing runtime by 92\%}
        \vspace{1.0mm}
        \item {Rearchitected task scheduling service and backend logging; improvements enabled recovery runs and task history queries}
        \vspace{1.0mm}
        \item {Released a new Go based image delivery and processing server and implemented an algorithm to dynamically generate matching backgrounds for book covers}
      \end{cvitems}
    }
  \vspace{2.4mm}    
  \cventry
    {software engineering intern (full stack)} % Job title
    {StackAdapt} % Organization
    {Toronto, ON} % Location
    {jan. - apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \vspace{1.0mm}
        \item {Optimized the main dashboard by creating a custom SQL statement assembler and reduced page loading times by 91\%}
        \vspace{1.0mm}
        \item {Developed features in Rails such as supporting multiple user sessions, an internal beta mode, new statistics reporting, and created React components for front-end rework}
        \vspace{1.0mm}
        \item {Integrated a geolocation mapping API and OS version filtering to a performant Go ad-exchange bidding service}
        \vspace{1.0mm}
        \item {Prototyped a service to capture live browser screenshots to provide insight into client advertisement displays}
      \end{cvitems}
    }
  \vspace{2.4mm}
  \cventry
    {software engineering intern (full stack)} % Job title
    {Street Contxt} % Organization
    {Toronto, ON} % Location
    {may - aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \vspace{1.0mm}
        \item {Shipped features in Play such as content bookmarking, integrating a client CSM database, new internal metric reports, and React updates for a platform overhaul}
        \vspace{1.0mm}
        \item {Built an Akka microservice to track interaction times via tracking pixels, utilizing Datadog for metrics monitoring}
        \vspace{1.0mm}
        \item {Expanded client notifitcations functionality by building and optimizing customized statistics reports}
      \end{cvitems}
    }
  \vspace{2.4mm}
  \cventry
    {Innovation Engineer Intern (full stack)} % Job title
    {CIBC Live Labs} % Organization
    {Toronto, ON} % Location
    {sep. - dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \vspace{1.0mm}
        \item {Developed an Android banking portfolio overview app and built a RESTful API for a backend service using Spring}
        \vspace{1.0mm}
        \item {Prototyped an Android app using Firebase, OCR, and Socket.IO to perform bill splitting sessions and background payments}
      \end{cvitems}
    }
  \vspace{2.4mm}
  \cventry
    {Applications Developer Intern (android)} % Job title
    {Shoppers Drug Mart Innovation} % Organization
    {Toronto, ON} % Location
    {jan. - mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \vspace{1.0mm}
        \item {Finished and released an Android pharmacy ailment diagnosis tool; estimated at \$10 million in outsourced development}
        \vspace{1.0mm}
        \item {Implemented a head office check-in system using an Android app and a Google RESTful Apps Script Execution API}
      \end{cvitems}
    }    
\end{cventries}
